Construction of replicated designs based on Sobol' sequences

### 2016-05-13 crass/crass.tex
Finshing to review crass

\selectlanguage{english}
\author[authorlabel1]{Laurent Gilquin},
\ead{laurent.gilquin@inria.fr}
\author[authorlabel2]{Llu\'{i}s Antoni Jim\'{e}nez Rugama},
%\ead{ljimene1@hawk.iit.edu}
\author[authorlabel3]{Elise Arnaud},
\author[authorlabel2]{Fred J. Hickernell},
\author[authorlabel4]{Herv\'{e} Monod},
\author[authorlabel3]{Cl\'{e}mentine Prieur}

\address[authorlabel1]{Inria Grenoble - Rh\^{o}ne-Alpes, Inovall\'{e}e, 655 avenue de l'Europe, 38330 Montbonnot}
\address[authorlabel2]{Illinois Institute of Technology}
\address[authorlabel3]{Univ. Grenoble Alpes, Jean Kunzmann Laboratory, F-38000 Grenoble, France \\
CNRS, LJK, F-38000 Grenoble, France, Inria}
\address[authorlabel4]{MaIAGE, INRA, Universit\'{e} Paris-Saclay, 78350 Jouy-En-Josas, France}

@@

\selectlanguage{francais}
% Text of abstract in French
\noindent{\bf R\'esum\'e} \vskip 0.5\baselineskip \noindent
{ \bf Construction de plans r\'epliqu\'es \`a partir de s\'equences de Sobol'.}
%{\bf Plans r\'epliqu\'es \`a base de s\'equences de Sobol' pour estimer les effets principaux des param\`etres d'un mod\`ele. }
Dans le contexte d'estimer les effets principaux des param\`etres d'un mod\`ele, nous proposons d'\'etudier deux approches pour construire des plans r\'epliqu\'es \`a partir de s\'equences de Sobol'.
{\it Pour citer cet article~: L. Gilquin, L. A. J. Rugama, E. Arnaud, F. J. Hickernell, H. Monod, C. Prieur, C. R. Acad. Sci.
Paris, Ser. I 340 (2005).}

@@

\section{Introduction}
Mathematical models used in various fields often involve a substantial number of poorly known parameters. The effect of these parameters on the output of the model can be assessed through sensitivity analysis. Global sensitivity analysis methods are useful tools to identify the parameters having the most influence on the output. A well known approach is the variance based method introduced by Sobol' \cite{Sobol2}. This method estimates sensitivity indices called Sobol' indices that summarize the influence of each model input. In particular, one can distinguish first-order indices that estimate the main effect of each input.

The procedure proposed by Sobol' to estimate first-order Sobol' indices and its improvements (see Saltelli \cite{Saltelli} for an exhaustive survey) all suffer from a prohibitive cost of model evaluations that grows with respect to the input space dimension. %An elegant solution to reduce this cost relies on the construction of replicated designs introduced by McKay \cite{mckay}.  
 An elegant solution to reduce this cost relies on the construction of particular design of experiments called replicated designs. The notion of replicated designs was first introduced by McKay through its introduction of replicated Latin Hypercubes \cite{Mckay}. 
Here, we define replicated designs in a wider framework:

\begin{definition}%[Replicated designs]
\label{rep.designs}
Denote by $\vx \in [0,1)^s$ a point with components $x_1,\dots,x_s$ and $\mathcal{D}=\{1,\dots,s\}$. Let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two point sets,
$\vx_i,\vx'_i\in[0,1)^{s}$. Let $\mathcal{P}^u=\{\vx_{i,u}\}_{i=0}^{n-1}$ (resp. $\mathcal{P}'^u$), $u \subsetneq \mathcal{D}$, denote the subset of dimensions of $\mathcal{P}$ (resp. $\mathcal{P}'$) indexed by $u$. We say that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $r$ if:\\
$\forall \ u \subsetneq \mathcal{D}$ such that $|u|=r$, $\mathcal{P}^u$ and $\mathcal{P}'^u$ are the same point set in $[0,1)^r$.
\end{definition}

With the construction of only two replicated designs of order $1$, the replication procedure introduced and studied in \cite{Mara,Tissot} allows to estimate all first-order Sobol' indices. This procedure has the major advantage of reducing drastically the estimation cost as the number of runs (one design $\mathcal{P}$ of size $n$  and its replication $\mathcal{P}'$) becomes independent of the input space dimension. However, Sobol' indices estimates may still not be accurate enough if the input space is not properly explored.
\bigskip

In this note, we propose to construct two replicated points sets based on Sobol' sequences that identify as two space-filling replicated designs of order $1$. These two designs insure that the input space is properly explored and can then be used within the replication procedure to estimate all main-effects of a numerical model. We first provide backgrounds on digital sequences, then we present two iterative approaches to construct the two replicated point sets.

@@

Replicated design properties can apply to digital sequences. Therefore, we introduce the definition,
\begin{definition}
Two digital sequences $\{\vx_i\}_{i\in\mathbb{N}_0}$ and $\{{\vx'}_i\}_{i\in\mathbb{N}_0}$ are said \emph{digitally replicated} of order $r$ if for all $m\geq 0$, $\{{\vx}_i\}_{i=0}^{b^m-1}$ and $\{{\vx'}_i\}_{i=0}^{b^m-1}$ are two replicated designs of order $r$.
\end{definition}

@@

$s$-dimensional Sobol' sequences are designed in base $b=2$ and can be computed using the \emph{generating matrices}, a set of $s$ full rank infinite dimensional upper triangular matrices defined over $\mathbb{F}_2:=\{0,1\}$. In \cite{Kuo}, Kuo and Joe suggest a particular choice for these matrices that optimize the 2 dimensional projection $t$-values.

We denote these matrices by $C_1,\dots,C_s$, and $C_1^m,\dots,C_s^m$ their upper left corner blocks of size $m\times m$. Although $C_1,\dots,C_s$ have infinite size, one only requires the knowledge of $C_1^m,\dots,C_s^m$ to construct the first $2^m$ points.

For each $i=0,\dots,2^m-1$, the point $\vx_i = (x_{i,1},\dots,x_{i,s})^\intercal$ of the sequence is obtained dimension-wise by:
\begin{equation}
\label{dig.net.eq.}
(x_{i,j,1},x_{i,j,2},\dots)^\intercal = C_j^{m} \vi,\qquad j= 1,\dots,s\, ,
\end{equation}
where $x_{i,j} = \sum_{k \geq 1}x_{i,j,k}2^{-k}$ and $\vi = (i_{0},\dots,i_{m-1})^\intercal$ the binary decomposition of $i$. Below we show how to compute $x_{11,1}=0.8125$ and $x_{9,2}=0.4375$

\begin{equation*}
\begin{pmatrix}
x_{11,1,1} \\
x_{11,1,2} \\
x_{11,1,3} \\
x_{11,1,4}
\end{pmatrix} =
\begin{pmatrix}
1 \\
1 \\
0 \\
1
\end{pmatrix} = 
\overbrace{
\begin{pmatrix}
1 & 0 & 0 & 0 \\
0 & 1 & 0 & 0 \\
0 & 0 & 1 & 0 \\
0 & 0 & 0 & 1
\end{pmatrix}}^{C_1^4}
\overbrace{
\begin{pmatrix}
1 \\
1 \\
0 \\
1
\end{pmatrix}}^{\bvec{11}},\qquad
\begin{pmatrix}
x_{9,2,1} \\
x_{9,2,2} \\
x_{9,2,3} \\
x_{9,2,4}
\end{pmatrix} =
\begin{pmatrix}
0 \\
1 \\
1 \\
1
\end{pmatrix} = 
\overbrace{\begin{pmatrix}
1 & 1 & 1 & 1 \\
0 & 1 & 0 & 1 \\
0 & 0 & 1 & 1 \\
0 & 0 & 0 & 1
\end{pmatrix}}^{C_2^4}
\overbrace{\begin{pmatrix}
1 \\
0 \\
0 \\
1
\end{pmatrix}}^{\bvec{9}}
\end{equation*}
\bigskip

Remark that for any $m' > m$, the matrix $C_j^m$ is embedded in the upper left of matrix $C_j^{m'}$. Resulting from this embedding, the next $2^m$ points of the digital sequence are constructed by increasing $m$ by one in equation (\ref{dig.net.eq.}). The process is iterated as many times as needed.

\begin{lemma}\label{Sobol_replicated}
All Sobol' sequences are digitally replicated of order 1.
\end{lemma}
\begin{pf*}{Proof.}
Consider any two $s$-dimensional Sobol' sequences generated by the generating matrices $C_1,\dots,C_s$ and $C'_1,\dots,C'_s$ respectively. Since these matrices are upper triangular, to compute the first $2^m$ points one only needs the knowledge of the $m\times m$ upper left blocks $C_j^m$ and ${C'}_j^m$, $j \in \{1,\dots,s\}$. Because any two matrices $C^{m}_j$ and ${C'}^{m}_j$ are square and full rank, the operations $C^{m}_j\vi$ and ${C'}^{m}_j\vi$ are one-to one and onto, for all $i=0,\dots,2^m-1$. Therefore, they generate the same point sets.
\end{pf*}

@@

\section{Iterative construction of replicated point sets}
SCRAMBLING
We propose here two approaches to construct two replicated point sets $\mathcal{P}$ and $\mathcal{P}'$ based on Sobol' sequences. These two constructions are iterative that is the two points sets constructed possess the following structure:
$$\mathcal{P}= B_1 \cup B_2 \cup B_3 \dots $$
$$\mathcal{P}'= {B'}_1 \cup {B'}_2 \cup {B'}_3 \dots $$
where $B_l$ (resp. $B'_l$), $l\geq1$, is a new set of points added at step $l$ to refine $\mathcal{P}$ (resp. $\mathcal{P}'$). For each approach and at each step, $\mathcal{P}$ and $\mathcal{P'}$ are two replicated designs of order $1$.

The first approach is called multiplicative approach and simply consists in generating two different Sobol' sequences. This approach exploits the result of Lemma \ref{Sobol_replicated}. The second approach is called additive approach. It takes an initial number of points of a Sobol' sequence and applies to it digital shift and scrambling operations to generate the two replicated points sets.

@@

The two replicated points sets $\mathcal{P}$ and $\mathcal{P}'$ constructed with the multiplicative approach are two $s$-dimensional Sobol' sequences constructed with different sets of generating matrices. We note $C_1,\dots,C_s$ the generating matrices used to generate design $\mathcal{P}$ and ${C'}_1,\dots,{C'}_s$ those used to generate design $\mathcal{P}'$. Our choice of the $2s$ generating matrices $C_1,\dots,C_S,{C'}_1,\dots,{C'}_s$ follows the results obtained by Joe and Kuo in \cite{Kuo}. These two authors proposed a set of generating matrices optimized based on the $t$-value of pairwise projections of the corresponding digital sequence. Here, we select $2s$ generating matrices from this set to generate our two designs $\mathcal{P}$ and $\mathcal{P}'$.
\bigskip

The iterative construction of designs $\mathcal{P}$ and $\mathcal{P}'$ proceed as follows:

at step $l$, $l \geq 1$, design $\mathcal{P}$ is refined with a set of $2^l$ points $B_l=\{\vx_{2^{l-1}},\dots,\vx_{2^l-1}\}$ obtained through equation (\ref{dig.net.eq.}) with $C_1^l,\dots,C_s^l$. Likewise, design $\mathcal{P}'$ is refined with ${B'}_l=\{\vx'_{2^{l-1}},\dots,\vx'_{2^l-1}\}$ obtained through equation (\ref{dig.net.eq.}) with ${C'}_1^l,\dots,{C'}_s^l$.

As a direct consequence of Lemma \ref{Sobol_replicated}, at each step $l$ the designs $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $1$. Furthermore, they both inherit the space-filling properties of $(t,l,s)$-nets.

@@

With the multiplicative approach, the sizes of designs $\mathcal{P}$ and $\mathcal{P}'$ are multiplied by $2$ at each step. This growth rate may be inadequate for some applications. The additive approach presented here is attractive due to the slow growing size of the two replicated designs $\mathcal{P}$ and $\mathcal{P}'$ constructed. At each step, only $2^m$ points are added to both designs. However, the main drawback is that $\mathcal{P}$ and $\mathcal{P}'$ each as a whole does not possess the structure of a Sobol' sequence anymore.
\bigskip

The two replicated points sets $\mathcal{P}$ and $\mathcal{P}'$ constructed with the additive approach are iteratively refined with new points sets $B_l$ and ${B'}_l$ that each possesses the structure of a $(t,m,s)$-net.

First, an initial set $B_0=\{\vx_i^{(0)}\}_{i=0}^{2^m-1}$ of $2^m$ points of a $s$-dimensional Sobol' sequence is generated by fixing $m >0$ and choosing $s$ generating matrices $C_1,\dots,C_s$. These matrices are selected from the set obtained in \cite{Kuo}. Then, at step $l$, $B_l$ and ${B'}_l$ are obtained from $B_0$ by carrying out digital shift and scrambling operations. These operations guarantee that both $B_l$ and ${B'}_l$ inherit the $(t,m,s)$-net structure of the initial set $B_0$. We detail below the construction of $B_l$ and ${B'}_l$.
\bigskip

At step $l$, $l \geq 1$, $B_l=\{\vx_i^{(l)}\}_{i=0}^{2^m-1}$ is generated by applying a digital shift to $B_0$:

for each $i=0,\dots,2^m-1$, the points $\vx_i^{(l)} = (x_{i,1}^{(l)},\dots,x_{i,s}^{(l)})^\intercal$ is obtained by:
\begin{equation}
\label{dig.shift}
(x_{i,j,1}^{(l)},\dots,x_{i,j,m}^{(l)})^\intercal = (x_{i,j,1}^{(0)},\dots,x_{i,j,m}^{(0)})^\intercal+\ve_j,\qquad j= 1,\dots,s\, ,
\end{equation}
where $ x_{i,j}^{(l)}=\sum_{k = 1}^mx_{i,j,k}^{(l)}2^{-k}$ and $\ve_j=(e_{j,{0}},\dots,e_{j,{m-1}})^\intercal \in ker(C_j^m)$ the kernel of $C_j^m$.
\bigskip

Then, ${B'}_l=\{{\vx'}_i^{(l)}\}_{i=0}^{2^m-1}$ is obtained from $B_l$ by applying Tezuka's i-binomial scrambling \cite{Tezuka}. This scrambling operation writes as follows:

for each $i=0,\dots,2^m-1$, the points ${\vx'}_i^{(l)} = ({x'}_{i,1}^{(l)},\dots,{x'}_{i,s}^{(l)})^\intercal$ is obtained by:
\begin{equation}
\label{ibinom.scrambling}
({x'}_{i,j,1}^{(l)},\dots,{x'}_{i,j,m}^{(l)})^\intercal = L_j^m (x_{i,j,1}^{(l)},\dots,x_{i,j,m}^{(l)})^\intercal,
\end{equation}
where $ {x'}_{i,j}^{(l)}=\sum_{k = 1}^m{x'}_{i,j,k}^{(l)}2^{-k}$ and $L_j^m$ is a full rank lower triangular matrix of size $m \times m$ over the Galois field $\mathbb{F}_2$.
\bigskip

@@

\begin{lemma}
At each step $l$, $l\geq1$, the digital shift and scrambling operations carried out in equations (\ref{dig.shift}) and (\ref{ibinom.scrambling}) ensure that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $1$. 
\end{lemma}

\begin{pf*}{Proof.}
This is a direct consequence of the following result: at each step $l$, $B_l$ and ${B'}_l$ are two replicated designs of order $1$. Indeed, since digital shift and i-binomial scrambling operations are bijections from ${\mathbb{F}_2}^m$ to ${\mathbb{F}_2}^m$, each dimension of $B_l$ and ${B'}_l$ contains the same set of $2^m$ values.
\end{pf*}

@@

>>>>

\selectlanguage{english}
\author[authorlabel1]{Laurent Gilquin},
\ead{laurent.gilquin@inria.fr}
\author[authorlabel2]{Llu\'{i}s Antoni Jim\'{e}nez Rugama},
\ead{ljimene1@hawk.iit.edu}
\author[authorlabel3]{Elise Arnaud},
\author[authorlabel2]{Fred J. Hickernell},
\author[authorlabel4]{Herv\'{e} Monod},
\author[authorlabel3]{Cl\'{e}mentine Prieur}

\address[authorlabel1]{Inria Grenoble - Rh\^{o}ne-Alpes, Inovall\'{e}e, 655 avenue de l'Europe, 38330 Montbonnot}
\address[authorlabel2]{Illinois Institute of Technology, Rettaliata Engineering Center, 10 W 32st, Chicago, IL 60616}
\address[authorlabel3]{Univ. Grenoble Alpes, Jean Kunzmann Laboratory, F-38000 Grenoble, France \\
CNRS, LJK, F-38000 Grenoble, France, Inria}
\address[authorlabel4]{MaIAGE, INRA, Universit\'{e} Paris-Saclay, 78350 Jouy-En-Josas, France}

@@

\selectlanguage{francais}
% Text of abstract in French
\noindent{\bf R\'esum\'e} \vskip 0.5\baselineskip \noindent
{ \bf Construction de plans r\'epliqu\'es \`a partir de s\'equences de Sobol'.}
%{\bf Plans r\'epliqu\'es \`a base de s\'equences de Sobol' pour estimer les effets principaux des param\`etres d'un mod\`ele. }
Dans le contexte d'estimer les effets principaux des param\`etres d'un mod\`ele, nous proposons d'\'etudier deux approches pour construire des plans r\'epliqu\'es \`a partir de s\'equences de Sobol'.
{\it Pour citer cet article~: L. Gilquin, Ll. A. Jim\'enez Rugama, E. Arnaud, F. J. Hickernell, H. Monod, C. Prieur, C. R. Acad. Sci.
Paris, Ser. I 340 (2005).}

@@

\section{Introduction}
Mathematical models often involve a substantial number of poorly known parameters. The effect of these parameters to the output of the model can be assessed through sensitivity analysis. Global sensitivity analysis methods are useful tools to identify the parameters having the most influence on the output. A well known approach is the variance based method introduced by Sobol' in \cite{Sobol2}. This method estimates sensitivity indices called Sobol' indices that summarize the influence of each model input. In particular, one can distinguish first-order indices that estimate the main effect of each input.

The procedure proposed by Sobol' to estimate first-order Sobol' indices and its improvements (see Saltelli \cite{Saltelli} for an exhaustive survey) suffer from a prohibitive cost of model evaluations that grows with respect to the input space dimension. %An elegant solution to reduce this cost relies on the construction of replicated designs introduced by McKay \cite{mckay}.  
 An elegant solution to reduce this cost relies on the construction of particular design of experiments called replicated designs. The notion of replicated designs was first introduced by McKay through its introduction of replicated Latin Hypercubes in \cite{Mckay}. 
Below we define replicated designs in a wider framework:

\begin{definition}%[Replicated designs]
\label{rep.designs}
Denote by $\vx \in [0,1)^s$ a point with components $x_1,\dots,x_s$ and $\mathcal{D}=\{1,\dots,s\}$. Let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two point sets in
$[0,1)^{s}$. Let $\mathcal{P}^u=\{\vx_{i,u}\}_{i=0}^{n-1}$ (resp. $\mathcal{P}'^u$), $u \subsetneq \mathcal{D}$, denote the subset of dimensions of $\mathcal{P}$ (resp. $\mathcal{P}'$) indexed by $u$. We say that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $a$ if $\forall \ u \subsetneq \mathcal{D}$ such that $|u|=a$, $\mathcal{P}^u$ and $\mathcal{P}'^u$ are the same point set in $[0,1)^a$.
\end{definition}

The replication procedure introduced by \cite{Mara,Tissot} allows to estimate all first-order Sobol' indices with only two replicated designs of order $1$. This procedure has the major advantage of reducing the estimation cost as the number of model evaluations (one design $\mathcal{P}$ of size $n$  and its replication $\mathcal{P}'$) becomes independent of the input space dimension. However, Sobol' indices estimates may still not be accurate enough if the input space is not properly explored.
\bigskip

In this note, we propose the construction of two replicated point sets based on Sobol' sequences that identify as two space-filling replicated designs of order $1$. These two designs ensure that the input space is properly explored and can be used within the replication procedure to estimate all main-effects of a numerical model. We first provide a brief introduction on digital sequences and then present two iterative approaches to construct the two replicated point sets.

@@

Replicated design properties can apply to digital sequences. Therefore, we introduce the definition,
\begin{definition}
Two digital sequences $\{\vx_i\}_{i\in\mathbb{N}_0}$ and $\{{\vx'}_i\}_{i\in\mathbb{N}_0}$ are \emph{digitally replicated} of order $a$ if for all $m\geq 0$, $\{{\vx}_i\}_{i=0}^{b^m-1}$ and $\{{\vx'}_i\}_{i=0}^{b^m-1}$ are two replicated designs of order $a$.
\end{definition}

@@

$s$-dimensional Sobol' sequences are designed in base $b=2$ and can be computed using the \emph{generating matrices}, a set of $s$ full rank infinite dimensional upper triangular matrices over $\mathbb{F}_2:=\{0,1\}$. We will denote by $\oplus$ the addition in $\mathbb{F}_2:=\{0,1\}$. In \cite{Kuo}, Kuo  and Joe suggest a particular choice for these matrices that optimize the 2 dimensional projection $t$-values.

Consider the generating matrices $C_1,\dots,C_s$, and $C_1^m,\dots,C_s^m$ their upper left corner blocks of size $m\times m$. Although $C_1,\dots,C_s$ are of infinite size, one only requires the knowledge of $C_1^m,\dots,C_s^m$ to construct the first $2^m$ points: for each $i=0,\dots,2^m-1$, the point $\vx_i = (x_{i,1},\dots,x_{i,s})^\intercal$ of the sequence is obtained dimension-wise:
\begin{equation}
\label{dig.net.eq.}
(x_{i,j,1},\dots,x_{i,j,m})^\intercal = C_j^{m} \vi,\qquad j= 1,\dots,s\, ,
\end{equation}
where $x_{i,j} = \sum_{k \geq 1}x_{i,j,k}2^{-k}$ and $\vi = (i_{0},\dots,i_{m-1})^\intercal$ are the binary decompositions of $x_{i,j}$ and $i$, and matrix operations are performed in $\mathbb{F}_2$. Below we provide an example on how to compute $x_{11,1}=0.8125$ and $x_{9,2}=0.4375$,
\begin{equation*}
\begin{pmatrix}
x_{11,1,1} \\
x_{11,1,2} \\
x_{11,1,3} \\
x_{11,1,4}
\end{pmatrix} = 
\overbrace{
\begin{pmatrix}
1 & 0 & 0 & 0 \\
0 & 1 & 0 & 0 \\
0 & 0 & 1 & 0 \\
0 & 0 & 0 & 1
\end{pmatrix}}^{C_1^4}
\overbrace{
\begin{pmatrix}
1 \\
1 \\
0 \\
1
\end{pmatrix}}^{\bvec{11}}=
\begin{pmatrix}
1 \\
1 \\
0 \\
1
\end{pmatrix}
,\qquad
\begin{pmatrix}
x_{9,2,1} \\
x_{9,2,2} \\
x_{9,2,3} \\
x_{9,2,4}
\end{pmatrix} = 
\overbrace{\begin{pmatrix}
1 & 1 & 1 & 1 \\
0 & 1 & 0 & 1 \\
0 & 0 & 1 & 1 \\
0 & 0 & 0 & 1
\end{pmatrix}}^{C_2^4}
\overbrace{\begin{pmatrix}
1 \\
0 \\
0 \\
1
\end{pmatrix}}^{\bvec{9}} =
\begin{pmatrix}
0 \\
1 \\
1 \\
1
\end{pmatrix}
\end{equation*}
\bigskip

To compute the next $2^m$ points of the sequence, one can infer from equation (\ref{dig.net.eq.}) that \\$(x_{i+2^m,j,1},\dots,x_{i+2^m,j,m+1})^\intercal=(x_{i,j,1},\dots,x_{i+2^m,j,m},0)^\intercal\oplus {(c_j^{m+1})}^\intercal$, where $c_j^{m+1}$ is the last column of $C_j^{m+1}$.

\begin{lemma}\label{Sobol_replicated}
All Sobol' sequences are digitally replicated of order 1.
\end{lemma}
\begin{pf*}{Proof.}
Consider any two $s$-dimensional Sobol' sequences generated by $C_1,\dots,C_s$ and $C'_1,\dots,C'_s$ respectively. Since any two matrices $C^{m}_j$ and ${C'}^{m}_j$ are square and full rank, the operations $C^{m}_j\vi$ and ${C'}^{m}_j\vi$ are one-to one and onto for all $i=0,\dots,2^m-1$. Therefore, they generate the same point sets.
\end{pf*}

@@

\section{Iterative constructions of extensible replicated point sets of order 1}

In this section we propose two different approaches to construct extensible replicated point sets of order 1, $\mathcal{P}_m$ and $\mathcal{P}'_m$, based on Sobol' sequences. These two constructions are iteratively extended according to:
$$\mathcal{P}_m= B_0 \cup \dots \cup B_m\, ,$$
$$\mathcal{P}'_m= {B'}_0 \cup \dots \cup {B'}_m\, ,$$
where $B_m$ and $B'_m$, $m \geq 0$, are new sets of points added at step $m$ to refine $\mathcal{P}_{m-1}$ and $\mathcal{P}'_{m-1}$. For all $m$, $\mathcal{P}_m$ and $\mathcal{P'}_m$ are two replicated designs of order $1$.

The first approach is called multiplicative because $|P_m|=2^m$ while the second one with $|P_m|=m|B_0|$ is called additive. In the multiplicative case, we will directly use $2$ $s$-dimensional sequences as a result from Lemma \ref{Sobol_replicated}. However, for the additive case, we will consider an initial set of Sobol' points and apply different scramblings and digital shifts to extend the point sets. Additionally, in both cases one can randomize the points with Owen's scrambling \cite{OwenScrambling} as long as equal dimensions between $\mathcal{P}_m$ and $\mathcal{P}'_m$ share the same scrambling.

@@

Two replicated point sets of order 1 $\mathcal{P}_m$ and $\mathcal{P}'_m$ can be constructed using two $s$-dimensional Sobol' sequences. We note $C_1,\dots,C_s$ the generating matrices used to generate $\mathcal{P}_m$ and ${C'}_1,\dots,{C'}_s$ those used to generate $\mathcal{P}'_m$. All these matrices need to be different.
% Our choice of the $2s$ generating matrices $C_1,\dots,C_s,{C'}_1,\dots,{C'}_s$ follows the results obtained by Joe and Kuo in \cite{Kuo}. These two authors proposed a set of generating matrices optimized based on the $t$-value of pairwise projections of the corresponding digital sequence. Here, we select $2s$ generating matrices from this set to generate our two designs $\mathcal{P}$ and $\mathcal{P}'$.
\bigskip

In order to iteratively construct designs $\mathcal{P}_m$ and $\mathcal{P}'_m$, one just needs to compute $B_\ell=\{\vx_{2^{\ell-1}},\dots,\vx_{2^\ell-1}\}$ and ${B'}_\ell=\{\vx'_{2^{\ell-1}},\dots,\vx'_{2^\ell-1}\}$ for all $\ell=1,\dots,m$, with $B_0=B'_0=\{\bvec{0}\}$. Each set $B_\ell$ can be obtained applying equation (\ref{dig.net.eq.}) to $C_1,\dots,C_s$, and $B'_\ell$ using $C'_1,\dots,C'_s$.

As a direct consequence of Lemma \ref{Sobol_replicated}, at each step $\ell$ designs $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ are two replicated designs of order $1$. Furthermore, they both inherit the space-filling properties of $(t,\ell,s)$-nets.

@@

With the multiplicative approach, the size of designs $\mathcal{P}_m$ and $\mathcal{P}'_m$ is multiplied by $2$ each time $m$ is increased by one. This growth rate may be inadequate for some applications. The additive approach presented in this section is attractive due to a slower size growth. Given a particular choice of $r\geq 1$, only $|B_0|=2^r$ points are added to both designs at each step. However, the main drawback is that $\mathcal{P}_m$ and $\mathcal{P}'_m$ do not possess the structure of a Sobol' sequence when $m\geq 1$.
\bigskip

The two replicated point sets $\mathcal{P}_m$ and $\mathcal{P}'_m$ constructed with the additive approach are iteratively refined with $B_{m+1}$ and ${B'}_{m+1}$. Each $B_{m+1}$ and ${B'}_{m+1}$ are $(t,r,s)$-nets.

First, $B_0=\{\vx_i^{(0)}\}_{i=0}^{2^r-1}$ is set to be the first $2^r$ Sobol' points of a $s$-dimensional sequence. Then, $B_0'$, $B_\ell$ and ${B'}_\ell$, for $\ell\geq 1$, are obtained from $B_0$ by carrying out digital shifts and scrambling operations. These operations guarantee that both $B_\ell$ and ${B'}_\ell$ inherit the $(t,r,s)$-net structure of the initial set $B_0$. We detail below the construction of $B_\ell$ and ${B'}_\ell$.
\bigskip

At step $\ell$, $\ell \geq 1$, $B_\ell=\{\vx_i^{(\ell)}\}_{i=0}^{2^r-1}$ is generated by applying a digital shift to $B_0$:

for each $i=0,\dots,2^r-1$, points $\vx_i^{(\ell)} = (x_{i,1}^{(\ell)},\dots,x_{i,s}^{(\ell)})^\intercal$ are obtained by:
\begin{equation}
\label{dig.shift}
(x_{i,j,1}^{(\ell)},\dots,x_{i,j,r}^{(\ell)})^\intercal = (x_{i,j,1}^{(0)},\dots,x_{i,j,r}^{(0)})^\intercal\oplus \ve_j,\qquad j= 1,\dots,s\, ,
\end{equation}
where $ x_{i,j}^{(\ell)}=\sum_{k = 1}^r x_{i,j,k}^{(\ell)}2^{-k}$ and $\ve_j=(e_{j,{0}},\dots,e_{j,{r-1}})^\intercal\in\mathbb{F}_2^r$.
\bigskip

Then, ${B'}_\ell=\{{\vx'}_i^{(\ell)}\}_{i=0}^{2^r-1}$ is obtained from $B_\ell$ by applying Tezuka's i-binomial scrambling \cite{Tezuka}. This scrambling operation writes as follows:

for each $i=0,\dots,2^r-1$, points ${\vx'}_i^{(\ell)} = ({x'}_{i,1}^{(\ell)},\dots,{x'}_{i,s}^{(\ell)})^\intercal$ are obtained by:
\begin{equation}
\label{ibinom.scrambling}
({x'}_{i,j,1}^{(\ell)},\dots,{x'}_{i,j,r}^{(\ell)})^\intercal = L_j^r (x_{i,j,1}^{(\ell)},\dots,x_{i,j,r}^{(\ell)})^\intercal,
\end{equation}
where $ {x'}_{i,j}^{(\ell)}=\sum_{k = 1}^r {x'}_{i,j,k}^{(\ell)}2^{-k}$ and each $L_j^r$ is a full rank lower triangular matrix of size $r \times r$ over $\mathbb{F}_2$.
\bigskip

@@

\begin{lemma}
Using the additive construction, $\mathcal{P}_m$ and $\mathcal{P}'_m$ are two replicated designs of order $1$ for $m\geq 0$.
\end{lemma}

\begin{pf*}{Proof.}
For each $\ell\geq 1$, digital shift and scrambling operations carried out in equations (\ref{dig.shift}) and (\ref{ibinom.scrambling}) are bijections from $\mathbb{F}^r_2$ to $\mathbb{F}^r_2$. Hence, equal dimensions of $B_\ell$ and ${B'}_\ell$ will contain the same set of $2^m$ values.
\end{pf*}

@@

\bibitem{OwenScrambling} A. B. Owen, Scrambling Sobol' and Niederreiter-xing points, \emph{J. Complexity}, 14(4), 1998, pp. 466--489.
